---
output: html_document
params: 
    set_title: "My Title!"
    set_date: "2017-10-05"
title: "`r params$set_title`"
date: "`r params$set_date`"
author: "Characterization Laboratory, Natural Resources Canada"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```
 
## Sample Information
Sample ID: `r sample_id`

Sample Name: `r sample_name`

Analysis Date: `r analysis_date`

Acquisition Method: `r acquisition_method`

Data File: `r data_file_name`

Data Analysis Method: `r data_analysis_method`

Results File: `r results_file`

Operator Name: `r operator_name`


## Breakdown by Carbon Count
```{r echo=FALSE, results='asis'}
kable(by_c, caption="Aggregate Peak Sum by Carbon Atom Count")
```

## Breakdown by C & H Count
```{r echo=FALSE, results='asis'}
kable(by_ch, caption="Aggregate Peak Sum by Carbon and Hydrogen Count")
```

## Breakdown by All Atom Count
```{r echo=FALSE, results='asis'}
kable(by_all, caption=paste("Aggregate Peak Sum by Atomic Count for", paste(element_list, collapse = ", ")))

